Title Goes Here

### 2020-02-24 paper/paper.tex
Add tail recursion step to diagram and fix minor code formatting issue

%%
%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{amsmath}

@@

\begin{lstlisting}
import Data.Char (ord)

@@

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (findmark) [process, below of=start]{Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{Wrap with \ttt{Construct} and \ttt{ConstructAp}};

@@

  \draw [arrow] (start) -- (findmark);
  \draw [arrow] (findmark) -- node[anchor=east] {Primitive} (handleprim);
  \draw [arrow] (findmark) -- node[anchor=west] {Function application/non-prim var} (handleapp);
  \draw [arrow] (findmark) -- node[anchor=east] {\ttt{case}} (handlecase);

>>>>

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{amsmath}

@@

\begin{lstlisting}[deletekeywords={Ord}]
import Data.Char (ord)

@@

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start]{Transform tail recursion (if applicable)};
  \node (findmark) [process, below of=tailrec]{Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{Wrap with \ttt{Construct} and \ttt{ConstructAp}};

@@

  \draw [arrow] (start) -- (tailrec);
  \draw [arrow] (tailrec) -- (findmark);
  \draw [arrow] (findmark) -- node[anchor=east] {Primitive} (handleprim);
  \draw [arrow] (findmark) -- node[anchor=west] {Function application/non-prim var} (handleapp);
  \draw [arrow] (findmark) -- node[anchor=east] {\ttt{case}} (handlecase);
